Borel regularity for ODEs and Thimble Integrals

### 2024-02-06 exp-resurgence.tex
Sync before working on proof of main results

%\subsection{Stokes phenomenon}
%\begin{itemize}
%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
%\item The jump comes from the branch cut difference identity for hypergeometric functions.
%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
%\end{itemize}
\subsection{Plan of the paper}
The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform. The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{sec:reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}. Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}. Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one. 
We include two appendices: the first one (Appendix~\ref{airy-appendix}) contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject. The second one, Appendix~\ref{apx:generalities_ODEs}, reviews the main aspects of \cite{reg-sing-volterra}.  
%
\subsection{Acknowledgements}
This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

@@

%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular. Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity. Hence $\Phi$ is Borel-regularizable. In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$. In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity. 
\subsection{Borel regularity for level~$1$ ODEs}
%
From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Since the cirtical values are distinct, the transmonomials $\tilde{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame. Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}). To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}. For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.

@@

%\textcolor{orange}{hyperasymptotics \cite{Berry_Howls,Berry1991,Howls97,Howls}}
%\color{DarkTurquoise}
%These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{Berry_Howls} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}. In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,pham1988resurgence}.
%\color{black}
%%Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}). In a nutshell, we use that thimble integrals are generalized Laplace transforms, to show they are indeed Borel regular functions.  
%     
\section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
\subsection{The geometry of the Laplace transform}
Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain. In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces. Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
%
\subsubsection{Translation surfaces, briefly}
%
A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\cite{zorich2006flat}. A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$. The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$. We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture. This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
    \label{fig:translation_surface}
\end{figure}
%
\subsubsection{Direction}\label{transl:dir}
%
The translation structure gives $B$ a notion of direction as well as distance. Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$. At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description. To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$. In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
%

@@

%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\Lambda}$. Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
%%\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big) \]
%%for some constant $\lambda' \in \R$. It follows that
%%\begin{align*}
%%\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
%%\end{align*}
\textcolor{orange}{[Oops, looks like we can't keep $\Delta$ constant along the integration path if we want to recover something with a $|\zeta_\alpha|^{\sigma-1}$ singularity.]}
\end{proof}
\color{RoyalBlue}
\textcolor{orange}{[We might be able to remove the decay properties completely!]} The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}^\theta$ control the asymptotics of $\laplace_{\zeta, \alpha}^\theta f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. In addition, we'll set $\theta=0$ to keep the notation simpler, but the results hold for every angle $\theta$. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use \cite[Equation 1.5]{sternin1995borel}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\sigma > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\sigma) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \sigma}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
\color{black}
%
%
%
\subsection{The geometry of the Borel transform}\label{sec:geometry_borel}
The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
Here, we're thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}. We can get a function on $T^*_{\zeta = b}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_b$ defined by $\zeta = \zeta_b + b$:
\[ \laplace_{\zeta_b, 0}\left[\frac{\zeta_b^n}{n!}\right] = z^{-n-1}. \]

\color{orange}
\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
\color{black}
On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate. This formal inverse is called the {\em Borel transform}. To be more precise, the Borel transform $\borel_\zeta$ on $T^*_{\zeta = 0}B$ is the inverse of $\laplace_{\zeta,0}$ on monomials 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \left\{1, \zeta, \frac{1}{2!} \zeta^2, \frac{1}{3!} \zeta^3, \ldots\right\} \arrow{u}{\laplace_{\zeta, 0}}
\end{tikzcd}
\end{center}
and it extends to formal power series by linearity 
\begin{align*}
\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
\end{align*}
\begin{remark}
The definition of the Borel transform can be easily extended to fractional power of $z$: indeed notice that   
\[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
for every $\sigma\in\R\setminus\Z_{\leq 0}$. Thus 
\begin{align*}
\borel_\zeta(z^{-\sigma-1})\defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)} 
\end{align*}
and then extended by linearity to $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$. 
\end{remark}
%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}

@@

\subsection{Borel and Laplace transforms as algebra homomorphisms}

@@

\color{orange}
\begin{lemma}
    Let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C\llbracket z^{-1}\rrbracket$ 
\begin{itemize}
\item[i)] for every $\lambda\in (0,\infty)$, \[\borel_\zeta\big(z^\lambda \tilde{\Phi}\big)=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\tilde{\Phi}.\]
\item[ii)] for every $\lambda\in (0,\infty)$, \[\borel_\zeta\big(z^{-\lambda} \tilde{\Phi}\big)=\fracderiv{-\lambda}{\zeta}{0}\borel_\zeta\tilde{\Phi}.\]
%\item[iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta (z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
\item[iii)] for every $n\geq 0$ \[\borel_\zeta\big(\partial_z^{n} \tilde{\Phi}\big)=(-\zeta)^n\borel_\zeta\tilde{\Phi}.\]
\end{itemize} 
\end{lemma}
\begin{proof} 
The result of $i)$ follows from Lemma~\ref{lem:frac-deriv-Borel}. Then to prove the result of $ii)$, notice that for $\lambda\in (0,\infty)$ \[\fracderiv{-\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\tfrac{k!}{\Gamma(k-\lambda+1)},\] hence \[\borel_\zeta (z^\lambda \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\lambda}}{\Gamma(k-\lambda+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\lambda}}{k!}\tfrac{k!}{\Gamma(k-\lambda+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\fracderiv{-\lambda}{\zeta}{0}\zeta^k=\fracderiv{-\lambda}{\zeta}{0}\borel_\zeta\tilde{\Phi}.\]

(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by definition \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]

(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]

(v) see \cite[Lemma 5.10]{diverg-resurg-i}.

\end{proof}
%
\color{RoyalBlue}
Define a new coordinate $\zeta_\alpha$ on $B$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
\begin{align*}
\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
\end{align*}
we learn that
\begin{equation}
    %\label{change-chart}
    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
\end{equation}
%
\subsubsection{Rescaling of translation structure}
%
Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. From the calculation
\begin{align*}
\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
\end{align*}
we learn that
\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
%
\subsubsection{Action on integral operators}\label{L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
where $p$ is any point on the position domain $B$.

It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).

The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$. This extends the semigroup law:
\begin{align*}
\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
\end{align*}

%Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.

>>>>

%\subsection{Stokes phenomenon}
%\begin{itemize}
%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
%\item The jump comes from the branch cut difference identity for hypergeometric functions.
%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
%\end{itemize}
\subsection{Plan of the paper}
The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform. The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{sec:reg-decay}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}. Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}. Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one. 
We include two appendices: the first one (Appendix~\ref{airy-appendix}) contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject. The second one, Appendix~\ref{apx:generalities_ODEs}, reviews the main aspects of \cite{reg-sing-volterra}.  
%
\subsection{Acknowledgements}
This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

@@

%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular. Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity. Hence $\Phi$ is Borel-regularizable. In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$. In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity. 
\subsection{Borel regularity for level~$1$ ODEs}
%
From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Since the cirtical values are distinct, the transmonomials $\tilde{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame. Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}). To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}. For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}. \textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]}

@@

%\textcolor{orange}{hyperasymptotics \cite{Berry_Howls,Berry1991,Howls97,Howls}}
%\color{DarkTurquoise}
%These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{Berry_Howls} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}. In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,pham1988resurgence}.
%\color{black}
%%Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}). In a nutshell, we use that thimble integrals are generalized Laplace transforms, to show they are indeed Borel regular functions.  
%     
\section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
\subsection{The geometry of the Laplace transform}
Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain. In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces. Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^*B$.
%
\subsubsection{Translation surfaces, briefly}
%
A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\cite{zorich2006flat}. A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$. The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$. We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture. This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
    \label{fig:translation_surface}
\end{figure}
%
\subsubsection{Direction}\label{transl:dir}
%
The translation structure gives $B$ a notion of direction as well as distance. Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$. At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description. To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$. In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
%

@@

%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\Lambda}$. Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
%%\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big) \]
%%for some constant $\lambda' \in \R$. It follows that
%%\begin{align*}
%%\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
%%\end{align*}
\textcolor{orange}{[Oops, looks like we can't keep $\Delta$ constant along the integration path if we want to recover something with a $|\zeta_\alpha|^{\sigma-1}$ singularity.]}
\color{RoyalBlue}
\textcolor{orange}{[We might be able to remove the decay properties completely!]} The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}^\theta$ control the asymptotics of $\laplace_{\zeta, \alpha}^\theta f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. In addition, we'll set $\theta=0$ to keep the notation simpler, but the results hold for every angle $\theta$. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use \cite[Equation 1.5]{sternin1995borel}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\sigma > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\sigma) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \sigma}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
\subsection{The geometry of the Borel transform}\label{sec:geometry_borel}
The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
Here, we're thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}. We can get a function on $T^*_{\zeta = b}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_b$ defined by $\zeta = \zeta_b + b$:
\[ \laplace_{\zeta_b, 0}\left[\frac{\zeta_b^n}{n!}\right] = z^{-n-1}. \]
On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate. This formal inverse is called the {\em Borel transform}. To be more precise, the Borel transform $\borel_\zeta$ on $T^*_{\zeta = 0}B$ is the inverse of $\laplace_{\zeta,0}$ on monomials 
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \left\{1, \zeta, \frac{1}{2!} \zeta^2, \frac{1}{3!} \zeta^3, \ldots\right\} \arrow{u}{\laplace_{\zeta, 0}}
and it extends to formal power series by linearity 
\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
\begin{remark}
The definition of the Borel transform can be easily extended to fractional power of $z$: indeed notice that   
\[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
for every $\sigma\in\R\setminus\Z_{\leq 0}$. Thus 
\borel_\zeta(z^{-\sigma-1})\defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)} 
and then extended by linearity to $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$. 
\end{remark}
%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}

@@

\subsection{Borel and Laplace transforms as algebra homomorphisms}\label{sec:borel-laplace-homom}

@@
